### 2017-06-30 draft/unique-linear.tex
snapshot

\clearpage
\begin{mathpar}
  \begin{array}{|c|c||c|c||c|c|l}
    Q_a&Q_b&O_a&O_b&P_a&P_b& \\
    \hline
    P_a &\emptyset& \emptyset & \emptyset & P_a & \emptyset & \\
    O_a & \emptyset& O_a & \emptyset & \emptyset & \emptyset & \\
    P_a\cup\READ   &\emptyset& \subseteq\READ & \emptyset & P_a & \emptyset & \\
    \READ&\READ& \WRITE\in & \emptyset & \READ & \emptyset
                       &  \text{copy, propagate left to write}\\
    \WRITE &\READ& \WRITE\in & \emptyset & \WRITE\in & \emptyset
                       &\text{copy, propagate left to write} \\
  \end{array}

  \begin{array}{|c|c||c|c||c|c|l}
    Q_a&Q_b&O_a&O_b&P_a&P_b& \\
    \hline
    P_a & P_b & \emptyset & \emptyset & P_a & P_b & \\
    O_a & P_b & O_a & \emptyset & \emptyset & P_b & \\
    P_a\cup\READ   &P_b& \subseteq\READ & \emptyset & P_a & P_b & \\
    \READ&P_b\cup\READ& \WRITE\in & \emptyset & \READ & P_b
                       &  \text{copy, propagate left to write}\\
    \WRITE & P_b\cup\READ & \WRITE\in & \emptyset & \WRITE\in & P_b
                       &\text{copy, propagate left to write} \\
  \end{array}

  \begin{array}{|c|c||c|c||c|c|l}
    Q_a&Q_b&O_a&O_b&P_a&P_b& \\
    \hline
    P_a & O_b & \emptyset & O_b & P_a & \emptyset & \\
    O_a & O_b & O_a & O_b & \emptyset & \emptyset & \\
    P_a\cup\READ  & O_b & \subseteq\READ & O_b & P_a & \emptyset & \\
    \READ&O_b \cup\READ& \WRITE\in & O_b & \READ & \emptyset
                       &  \text{copy, propagate left to write}\\
    \WRITE &O_b\cup\READ& \WRITE\in & O_b & \WRITE\in & \emptyset
                           &\text{copy, propagate left to write} \\
  \end{array}

\begin{array}{|c|c||c|c||c|c|l}
    Q_a&Q_b&O_a&O_b&P_a&P_b& \\
    \hline
    P_a &\emptyset& \emptyset & \emptyset & P_a & \emptyset & \\
    O_a & \emptyset& O_a & \emptyset & \emptyset & \emptyset & \\
    P_a\cup\READ   &\emptyset& \subseteq\READ & \emptyset & P_a & \emptyset & \\
    \READ&\READ& \WRITE\in & \emptyset & \READ & \emptyset
                       &  \text{copy, propagate left to write}\\
    \WRITE &\READ& \WRITE\in & \emptyset & \WRITE\in & \emptyset
                       &\text{copy, propagate left to write} \\
  \end{array}
\end{mathpar}

>>>>

\clearpage
\begin{mathpar}
  \begin{array}{|c|c||c|c||c|c|l}
    Q_a&Q_b&O_a&O_b&P_a&P_b& \\
    \hline
    P_a &\emptyset& \emptyset & \emptyset & P_a & \emptyset & \\
    O_a & \emptyset& O_a & \emptyset & \emptyset & \emptyset & \\
    P_a\cup\READ   &\emptyset& \READ & \emptyset & P_a & \emptyset & \\
    \READ&\READ& \WRITE\in & \emptyset & \READ & \emptyset
                       &  \text{copy, propagate left to write}\\
    \WRITE &\READ& \WRITE\in & \emptyset & \WRITE\in & \emptyset
                       &\text{copy, propagate left to write} \\
  \end{array}

  \begin{array}{|c|c||c|c||c|c|l}
    Q_a&Q_b&O_a&O_b&P_a&P_b& \\
    \hline
    P_a & P_b & \emptyset & \emptyset & P_a & P_b & \\
    O_a & P_b & O_a & \emptyset & \emptyset & P_b & \\
    P_a\cup\READ   &P_b& \READ & \emptyset & P_a & P_b & \\
    \READ&P_b\cup\READ& \WRITE\in & \emptyset & \READ & P_b
                       &  \text{copy, propagate left to write}\\
    \WRITE & P_b\cup\READ & \WRITE\in & \emptyset & \WRITE\in & P_b
                       &\text{copy, propagate left to write} \\
  \end{array}

  \begin{array}{|c|c||c|c||c|c|l}
    Q_a&Q_b&O_a&O_b&P_a&P_b& \\
    \hline
    P_a & O_b & \emptyset & O_b & P_a & \emptyset & \\
    O_a & O_b & O_a & O_b & \emptyset & \emptyset & \\
    P_a\cup\READ  & O_b & \READ & O_b & P_a & \emptyset & \\
    \READ&O_b \cup\READ& \WRITE\in & O_b & \READ & \emptyset
                       &  \text{copy, propagate left to write}\\
    \WRITE &O_b\cup\READ& \WRITE\in & O_b & \WRITE\in & \emptyset
                           &\text{copy, propagate left to write} \\
  \end{array}

\begin{array}{|c|c||c|c||c|c|l}
    Q_a&Q_b&O_a&O_b&P_a&P_b& \\
    \hline
    P_a &P_b\cup\READ& \emptyset & \READ & P_a & P_b & \\
    O_a & P_b\cup\READ& O_a & \READ & \emptyset & P_b & \\
    P_a\cup\READ   &P_b\cup\READ& \READ & \READ & P_a & P_b & \\
    \READ&P_b\cup\READ& \WRITE\in & \READ & \READ & P_b
                       &  \text{copy, propagate left to write}\\
    \WRITE &P_b\cup\READ& \WRITE\in & \READ & \WRITE\in & P_b
                       &\text{copy, propagate left to write} \\
  \end{array}

  \begin{array}{|c|c||c|c||c|c|l}
    Q_a&Q_b&O_a&O_b&P_a&P_b& \\
    \hline
    P_a\cup\READ &\READ& \emptyset & \WRITE\in & P_a & \READ
                           & \text{copy, propagate left to write} \\
    \READ & \READ& O_a & \WRITE\in & \emptyset & \READ
                           & \text{copy, propagate left to write} \\
    P_a\cup\READ   &\READ& \READ & \WRITE\in & P_a & \READ
                           &  \text{copy, propagate left to write}\\
    \READ&\READ& \WRITE\in & \WRITE\in & \READ & \READ
                       &  \text{copy, propagate left to write}\\
    \WRITE &\READ& \WRITE\in & \WRITE\in & \WRITE\in & \READ
                       &\text{copy, propagate left to write} \\
  \end{array}

  \begin{array}{|c|c||c|c||c|c|l}
    Q_a&Q_b&O_a&O_b&P_a&P_b& \\
    \hline
    P_a\cup\READ &\WRITE& \emptyset & \WRITE\in & P_a & \WRITE\in
                           & \text{copy, propagate left to write} \\
    \READ & \WRITE& O_a & \WRITE\in & \emptyset & \WRITE\in
                           & \text{copy, propagate left to write} \\
    P_a\cup\READ   &\WRITE& \READ & \WRITE\in & P_a & \WRITE\in
                           &  \text{copy, propagate left to write}\\
    \READ&\WRITE& \WRITE\in & \WRITE\in & \READ & \WRITE\in
                       &  \text{copy, propagate left to write}\\
    \WRITE &\WRITE& \WRITE\in & \WRITE\in & \WRITE\in & \WRITE\in
                       &\text{copy, propagate left to write} \\
  \end{array}
\end{mathpar}
A copy operation reads \textbf{every} field. Hence, a copy operation
caused by one field implies a read effect on all fields.
